COSC-373 Final Report: Bitcoin

### 2022-05-12 paper/paper.tex
Add some emph.

The main idea behind digital signatures is as follows. Both Alice and Bob each
generate a private/public key pair for themselves, where each key is a string of
bits and private keys are kept secret (i.e., only Alice knows her private key
and only Bob knows his private key). Producing a signature involves a function
$\mathsf{sign(msg, priKey)}$, which takes Alice's message $\mathsf{msg}$ and
private key $\mathsf{priKey}$ as inputs and outputs Alice's signature
$\mathsf{sig}$. Similarly, verifying the authenticity of the received message
involves a function $\mathsf{verify(msg, sig, pubKey)}$, which takes the
received message $\mathsf{msg}$, the signature $\mathsf{sig}$, and Alice's
public key $\mathsf{pubKey}$ as inputs and outputs \emph{true} if the signature
was produced using Alice's message and private key, and \emph{false} otherwise.
We will not discuss how the $\mathsf{sign()}$ and $\mathsf{verify()}$ functions
work in depth since such details are not the focus of this work.

Digital signatures have two required properties. First, the authenticity of
Alice's signature generated from her message and private key can be verified
easily using her corresponding public key. Secondly, it should be
computationally infeasible for someone like Eve to generate a valid signature
for Alice without knowing Alice's private key. That is, Eve has no better
strategy than guessing and checking if random signatures are valid using Alice's
message and public key. Assuming a 256 bit signature, the aforementioned brute
force strategy would require Eve to check $2^{256}$ signatures in the worst
case.

>>>>

The main idea behind digital signatures is as follows. Both Alice and Bob each
generate a \emph{private key} and \emph{public key} pair for themselves, where
each key is a string of bits and private keys are kept secret (i.e., only Alice
knows her private key and only Bob knows his private key). Producing a signature
involves a function $\mathsf{sign(msg, priKey)}$, which takes Alice's message
$\mathsf{msg}$ and private key $\mathsf{priKey}$ as inputs and outputs Alice's
signature $\mathsf{sig}$. Similarly, verifying the authenticity of the received
message involves a function $\mathsf{verify(msg, sig, pubKey)}$, which takes the
received message $\mathsf{msg}$, the signature $\mathsf{sig}$, and Alice's
public key $\mathsf{pubKey}$ as inputs and outputs \emph{true} if the signature
was produced using Alice's message and private key, and \emph{false} otherwise.
We will not discuss how the $\mathsf{sign()}$ and $\mathsf{verify()}$ functions
work in depth since such details are not the focus of this work.

Digital signatures have two required properties. First, the authenticity of
Alice's signature generated from her message and private key can be
\emph{verified easily} using her corresponding public key. Secondly, it should
be \emph{computationally infeasible} for someone like Eve to generate a valid
signature for Alice without knowing Alice's private key. That is, Eve has no
better strategy than guessing and checking if random signatures are valid using
Alice's message and public key. Assuming a 256 bit signature, the aforementioned
brute force strategy would require Eve to check $2^{256}$ signatures in the
worst case.
